Are environmental and geographic effective surrogates for genetic variation in conservation planning?

### 2016-01-18 article/article.Rmd

<!-- NOTES -->
<!-- 6 page limit w/o incurring costs -->

@@

## Introduction
<!-- 200 word limit -->

@@

First, we grouped individuals into genetic lineages for each species (Figure S2). The purpose of this step was to avoid confounding variation between populations with due to genetic history with variation attributed to selection pressures. We used the Bayesian clustering method implemented in $\texttt{Structure}$ [version 2.3.4; @r461; @r462] assuming admixture and an independent alleles model. For each species, we identified the most plausible number of populations (K = `r min(structure.params.LST[[MODE]]$k)`--`r max(structure.params.LST[[MODE]]$k)`; `r structure.params.LST[[MODE]]$numruns` runs per K; `r structure.params.LST[[MODE]]$burnin` burn-in iterations; `r structure.params.LST[[MODE]]$numreps` post-burn-in iterations) using the $\Delta$K method [Figure S3; @r460]. We aggregated the population membership probabilities from replicate runs using $\texttt{CLUMPP}$ [version 1.1.2; large K greedy search method with `r clumpp.params.LST[[MODE]]$repeats` random starts per K per species; Figure S4; @r459]. Individuals with a moderate probability of belonging to a single population ($\geq `r structure.params.LST[[MODE]]$probthresh`$) were assigned accordingly (Figure S5), and subject to subsequent outlier locus detection methods.

@@

After classifying loci as adaptive or neutral, we mapped the main gradients of the adaptive (if present) and neutral genetic variation for each species (Figures S4--S29). Note that while individuals not assigned to populations were omitted from the $\texttt{Bayescan}$ analysis, here we used all the individuals. For each species, for each type of genetic variation present, we used Gower distances [@r464] to express the genomic differences between individuals [using the cluster R package to accommodate sparsity; @r457]. These distances were subject to a non metric multi-dimensional scaling analysis [implemented in the vegan R package using K=`r mds.params.LST[[MODE]]$k` and `r mds.params.LST[[MODE]]$trymax` random starts; Table S3; @r458]. The average of the ordinated values associated with individuals in each grid cell we used to characterize the genomic variation in the grid cell.

### Prioritizations
We used the unreliable representative and adequate prioritization (URAP) formulation of the reserve selection problem [@r465]. We treated the genomic and surrogate variables as distinct attribute spaces. We set the demand points for each species and its attribute space using the values associated with the planning units. First, we generated a set of single species prioritizations. For each species, we generated a prioritization using a `r (rapr.params.LST[[MODE]]$amount.target*100)`% amount-based target, a prioritization using a `r (rapr.params.LST[[MODE]]$amount.target*100)`% amount-based target and `r (rapr.params.LST[[MODE]]$surrogate.target*100)`% space-based targets for the surrogate variation, and a prioritization using a `r (rapr.params.LST[[MODE]]$amount.target*100)`% amount-based target and `r (rapr.params.LST[[MODE]]$genetic.target*100) `% space-based targets for the genomic variation. Next, we generated three multi-species prioritizations using the same sets of targets used in the single species prioritizations. Finally, to understand the relationship between the surrogate-based and genomic-based targets, we generated a suite of prioritizations using increasing space-based targets between `r (min(rapr.params.LST[[MODE]]$pareto.surrogate.targets)*100)`% and `r (max(rapr.params.LST[[MODE]]$pareto.surrogate.targets)*100)`% in increments of `r diff(rapr.params.LST[[MODE]]$pareto.surrogate.targets[1:2])*100`%. For each prioritization we calculated the proportion of the adaptive (if present) and neutral genetic variation that it secured. We solved the reserve selection problems to within `r (gurobi.params.LST[[MODE]]$MIPGap*100)`% of optimality using the $\texttt{rapr}$ R package [@r465] and $\texttt{Gurobi}$ [@r463].

>>>>

<!-- NOTES -->
<!-- 200 word limit for abstract -->
<!-- 6 page limit w/o incurring costs -->

@@

## Introduction

@@

First, we grouped individuals into genetic lineages for each species (Figure S2). The purpose of this step was to avoid confounding variation between populations attributed to genetic history instead of selection pressures. We used discriminant analyses of principle components [DAPC; @r467] to assign individuals to populations [implemented in \texttt{adegenet} R package; @r468]. Briefly, for each species, we transformed the binary loci data using a principle components analysis (PCA) and obtained the principle components required to explain at least `r adegenet.params.LST[[MODE]]$perc.pca`% variation. We subject these components to multiple $k$-means clustering models with varying numbers of assumed populations (1--`r adegenet.params.LST[[MODE]]$max.n.clust`; `r adegenet.params.LST[[MODE]]$n.inter` iterations; `r adegenet.params.LST[[MODE]]$n.start` random starts). We then  applied Ward's clustering method to the Bayesian Information Criterion (BIC) statistics associated with each model to partition the models into two groups. We selected the model before the first group switch, and used the population memberships in that model for subsequent analysis.

@@

After classifying loci as adaptive or neutral, we mapped the main gradients of the adaptive (if present) and neutral genetic variation for each species (Figures S4--S29). For each species, for each type of genetic variation present, we used Gower distances [@r464] to express the genomic differences between individuals [using the $\texttt{cluster}$ R package to accommodate sparsity; @r457]. These distances were subject to multiple non-metric multi-dimensional scaling analyses using the minimum number of dimensions required to acheive an adequate stress value  [`r mds.params.LST[[MODE]]$max.stress`; `r mds.params.LST[[MODE]]$trymax` random starts; Table S3; implemented in the \texttt{vegan} R package; @r458]. Since each grid cell had up to three samples per species, we used the average of the ordinated values associated with the samples in each grid cell to characterize the genomic variation among the grid cells.

### Prioritizations
We used the unreliable representative and adequate prioritization (URAP) formulation of the reserve selection problem [@r465]. This formulation can identify the minimum number of planning units required to preserve a proportion of the species' range as well as a proportion of the species' variation [using an attribute space; _sensu_ @r465]. We treated the genomic and surrogate variables as distinct attribute spaces. We set the demand points for each species and its attribute space using the values associated with the planning units.

To fulfil the aims of the study, we generated three sets of prioritisations. First, we generated a set of single species prioritizations. For each species, we generated a prioritization using a `r (rapr.params.LST[[MODE]]$amount.target*100)`% amount-based target, a prioritization using a `r (rapr.params.LST[[MODE]]$amount.target*100)`% amount-based target and `r (rapr.params.LST[[MODE]]$surrogate.target*100)`% space-based targets for the surrogate variation, and a prioritization using a `r (rapr.params.LST[[MODE]]$amount.target*100)`% amount-based target and `r (rapr.params.LST[[MODE]]$genetic.target*100) `% space-based targets for the genomic variation. Next, we generated three multi-species prioritizations using the same sets of targets used in the single species prioritizations. Finally, to understand the relationship between the surrogate-based and genomic-based targets, we generated a suite of prioritizations using increasing space-based targets between `r (min(rapr.params.LST[[MODE]]$pareto.surrogate.targets)*100)`% and `r (max(rapr.params.LST[[MODE]]$pareto.surrogate.targets)*100)`% in increments of `r diff(rapr.params.LST[[MODE]]$pareto.surrogate.targets[1:2])*100`%. All of these prioritisations had no amount-based targets. For each prioritization we calculated the proportion of the adaptive (if present) and neutral genetic variation that it secured. We solved the reserve selection problems to within `r (gurobi.params.LST[[MODE]]$MIPGap*100)`% of optimality using the $\texttt{rapr}$ R package [@r465] and $\texttt{Gurobi}$ [@r463].

## Statistical analysis
We tested for differences in the effectiveness of prioritisations at securing genomic variation using general linear models (GLMs). These models were fit to the proportion of genomic variation explained using a logit link. They contained a predictor variable indicating if the prioritisation was generated using amount, surrogate, or genetic targets, a second predictor variable indicating if the genomic variation was adaptive or neutral, and the interaction between these variables. These models were subject to stepwise term deletion routes using likelihood ratio tests (LRT) to identify the minimal adequate model (terms were retained when $P < 0.05$).

### 2016-01-18 article/supporting_information.Rmd

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each square represents a planning unit. The color of each planning unit panel corresponds to ordination values. Planning units with similar colors contain individiduals with similar genetic variation.')}
plot.spp.mds(1)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}. See Figure S6 caption for conventions.')}
plot.spp.mds(2)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}. See Figure S6 caption for conventions.')}
plot.spp.mds(3)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(4)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(5)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(6)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(7)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(8)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(9)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(10)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(11)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(12)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(13)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(14)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(15)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(16)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(17)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(18)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(19)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(20)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(21)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(22)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(23)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(24)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(25)
```
```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(26)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}. See Figure S6 caption for conventions.')}
# plot.spp.mds(27)
```

>>>>

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each square represents a planning unit. The color of each planning unit panel corresponds to ordination values. Planning units with similar colors contain individiduals with similar genetic variation.')}
if (1 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(1)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}. See Figure S6 caption for conventions.')}
if (2 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(2)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}. See Figure S6 caption for conventions.')}
if (3 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(3)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}. See Figure S6 caption for conventions.')}
if (4 <= general.params.LST[[MODE]]$n.spp) if (4 <= ) plot.spp.mds(4)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}. See Figure S6 caption for conventions.')}
if (5 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(5)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}. See Figure S6 caption for conventions.')}
if (6 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(6)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}. See Figure S6 caption for conventions.')}
if (7 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(7)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}. See Figure S6 caption for conventions.')}
if (8 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(8)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}. See Figure S6 caption for conventions.')}
if (9 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(9)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}. See Figure S6 caption for conventions.')}
if (10 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(10)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}. See Figure S6 caption for conventions.')}
if (11 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(11)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}. See Figure S6 caption for conventions.')}
if (12 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(12)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}. See Figure S6 caption for conventions.')}
if (13 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(13)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}. See Figure S6 caption for conventions.')}
if (14 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(14)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}. See Figure S6 caption for conventions.')}
if (15 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(15)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}. See Figure S6 caption for conventions.')}
if (16 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(16)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}. See Figure S6 caption for conventions.')}
if (17 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(17)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}. See Figure S6 caption for conventions.')}
if (18 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(18)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}. See Figure S6 caption for conventions.')}
if (19 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(19)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}. See Figure S6 caption for conventions.')}
if (20 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(20)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}. See Figure S6 caption for conventions.')}
if (21 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(21)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}. See Figure S6 caption for conventions.')}
if (22 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(22)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}. See Figure S6 caption for conventions.')}
if (23 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(23)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}. See Figure S6 caption for conventions.')}
if (24 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(24)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}. See Figure S6 caption for conventions.')}
if (25 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(25)
```
```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}. See Figure S6 caption for conventions.')}
if (26 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(26)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}. See Figure S6 caption for conventions.')}
if (27 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(27)
```
